choosing_best

### 2021-02-21 choosing_significant_harmonies.Rmd
restructure section on normalisation

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(here)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(here)
library(hakear)
library(tidyr)
library(distributional)
library(dplyr)
library(ggplot2)
```

@@

```{r varall}

sim_varall_normal <- function(nx, nfacet, mean, sd, w) {
  dist_normal((mean + seq(0,
    (nx *
      nfacet - 1),
    by = 1
  ) * w), sd)
}
sim_panel_varall <- sim_panel(
  nx = 2, nfacet = 3,
  ntimes = 500,
  sim_dist = sim_varall_normal(2, 3, 0, 1, 10)
) %>% unnest(data)

set.seed(9999)
varall <- compute_pairwise_norm(sim_panel_varall, 
                           gran_x = "id_x",
                           gran_facet = "id_facet",
                           response = sim_data, 
                           nperm = 200
)

# plot
p_varall <- sim_panel_varall %>%
  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
```

```{r varx}
sim_varx_normal <- function(nx, nfacet, mean, sd, w) {
   rep(dist_normal((mean + seq(0, nx - 1, by = 1) * w), sd), nfacet)
 }

sim_panel_varx <- sim_panel(
   nx = 2, nfacet = 3,
   ntimes = 5,
   sim_dist = sim_varx_normal(2, 3, 0, 1, 10)
 ) %>% unnest(data)

set.seed(9999)
varx <- compute_pairwise_norm(sim_panel_varx, 
                           gran_x = "id_x",
                           gran_facet = "id_facet",
                           response = sim_data, 
                           nperm = 200
)

# plot
p_varx <- sim_panel_varx %>%
  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
```

```{r varf}
sim_varf_normal <- function(nx, nfacet, mean, sd, w) {
  rep(dist_normal((mean + seq(0, nfacet - 1, by = 1) * w), sd), each = nx)
}
sim_panel_varf <- sim_panel(
  nx = 2, nfacet = 3,
  ntimes = 5,
  sim_dist = sim_varf_normal(2, 3, 0, 1, 10)
) %>% unnest(data)

set.seed(9999)
varf <- compute_pairwise_norm(sim_panel_varf, 
                           gran_x = "id_x",
                           gran_facet = "id_facet",
                           response = sim_data, 
                           nperm = 200
)

p_varf <- sim_panel_varf %>%
  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
```

```{r null}
sim_panel_null <- sim_panel(
   nx = 2,
   nfacet = 3,
   ntimes = 500,
   sim_dist = distributional
   ::dist_normal(0, 1)
) %>% unnest(c(data))

set.seed(9999)

null <- compute_pairwise_norm(sim_panel_null, 
                           gran_x = "id_x",
                           gran_facet = "id_facet",
                           response = sim_data, 
                           nperm = 200
)

p_null <- sim_panel_null %>%
  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot()
```
